## **Part B - Deep Dive – WHO `r selected.region` Region**

## **WHO `r selected.region`: Trend - RRA, EIS, DON by month**

```{r, include=FALSE}
# REGION PROCESSING
df_regions <- read.csv('country_region.csv') %>%
  as.data.frame(.) %>%
  rename(country=countryName,
         region=Region) %>%
  mutate(region = 
           ifelse(country %in% c('AMERICAN SAMOA', 'GUAM'), 'AMRO', region),
         country=toupper(country))

df_regions_parentheses <- df_regions %>% 
  filter(grepl(' \\((.*?)\\)', country)) %>% 
  mutate(country = ifelse(grepl('HONG KONG', country), 'HONG KONG', country),
         country = ifelse(grepl('MACAO', country), 'MACAO', country),
         country = ifelse(grepl('TAIWAN', country), 'TAIWAN', country),
         country = str_remove(country, ' \\((.*?)\\)')) #Removes the parentheses

df_regions_more_countries <- df_regions %>%
  filter(grepl('UNITED STATES OF AMERICA|CÔTE|BOLIVIA|UNITED KINGDOM|CHINA ', country)) %>%
  arrange(country) %>%
  mutate(country = c('BOLIVIA (PLURINATIONAL STATE OF)', 
                     'COTE D\'IVOIRE',
                     'CHINA, HONG KONG',
                     'CHINA, MACAO',
                     'CHINA, PROVINCE OF TAIWAN',
                     'UNITED KINGDOM OF GREAT BRITAIN AND NORTHERN IRELAND',
                     'UNITED STATES')) %>%
  add_case(country='UK', iso3='GBR', iso2='GB', region='EURO') #Example of how to add more cases by hand


# Add countries with different formats
df_regions <- rbind(df_regions,
                    df_regions_parentheses,
                    df_regions_more_countries) %>%
  distinct(.keep_all = T)


# Recode country names so that it's easier to manipulate 
df_pt$country <- toupper(df_pt$country)

df_pt2 <- df_pt %>%
  mutate(region = NA)

for(country.query in df_regions$country){
  
  pos <- grep(toupper(country.query), toupper(df_pt2$country))
  
  if(length(pos) >= 1){
    df_pt2$region[pos] <- df_regions %>% 
      filter(country==country.query) %>% 
      pull(region)
  }
  
  # Exception for SOUTH SUDAN
  df_pt2$region[which(toupper(df_pt2$country)=='SOUTH SUDAN')] <- 'AFRO'
}


# Countries with empty region and not MULTIPLE
df_pt_unmatched <- df_pt2 %>%
  filter(is.na(region) & country!='MULTIPLE') %>%
  select(country, region)

if(nrow(df_pt_unmatched) >=1){
  unmatched_countries <- df_pt2 %>%
    filter(is.na(region) & country!='MULTIPLE') %>%
    pull(country)
} else {
  unmatched_countries <- 'No unmatched countries.'
}


# Recode country_region
for(country.query in df_regions$country){
  pos <- grep(ifelse(nchar(country.query)==2, 
                     country.query,
                     simpleCap(country.query)), 
              df_pt2$country_region)
  
  if(length(pos)>=1){
    region <- df_regions %>% filter(country==country.query) %>% pull(region)
    
    df_pt2$country_region[pos] <- str_replace(df_pt2$country_region[pos],
                                              ifelse(nchar(country.query)==2, 
                                                     country.query,
                                                     simpleCap(country.query)), 
                                              region)
  }
}


# Filter for the region - rbinds filter for selected.region in region or in country.region
df_pt_region <- rbind(
  
  df_pt2 %>%
    filter(region==toupper(selected.region)),
  
  df_pt2 %>%
    filter(is.na(region) & grepl(toupper(selected.region), toupper(country_region)))
)


if(selected.region=='Global'){
  df_pt_region <- df_pt2 %>%
    filter(grepl('Global|GLOBAL|global', region) | grepl('Global|GLOBAL|global', country_region))
}

```


```{r include=FALSE}
# DON TRACKER PROCESSING
# Filter the DON tracker
df_don_region <- df_don %>% 
  mutate(region = str_replace_all(region, 'PAHO', 'AMRO')) %>%
  filter(grepl(toupper(selected.region), toupper(region)))

# Position of nmatched regions in DON
don.unmatched.regions.pos <- which(grepl('AFRO|EMRO|SEARO|EURO|WPRO|PAHO|MULTIPLE',
                                         toupper(df_don$region))==FALSE)


# Fetch the regions of the countries with no region
don.unmatched.regions.fetch <- c()
for(country.query in df_don$country[don.unmatched.regions.pos]){
  don.unmatched.regions.fetch <- c(
    
    don.unmatched.regions.fetch,
    
    ifelse(length(df_regions$region[toupper(df_regions$country)==toupper(country.query)])==0, 
           NA,      
           df_regions$region[df_regions$country==country.query])
  )
}


# Change the regions
df_don_unmatched <- df_don[don.unmatched.regions.pos,] %>%
  mutate(region = don.unmatched.regions.fetch) %>% 
  filter(DON_pub_year_month >= as.Date(as.yearmon(report.month)) %m-% months(4)&
           DON_pub_year_month < as.Date(as.yearmon(report.month)) %m+% months(2))


# Add the fetched regions to the df_don_region
df_don_unmatched_region <- df_don_unmatched %>%
  filter(DON_pub_year_month >= as.Date(as.yearmon(report.month)) %m-% months(4)&
           DON_pub_year_month < as.Date(as.yearmon(report.month)) %m+% months(2)) %>% 
  filter(grepl(toupper(selected.region), toupper(region)))

if(nrow(df_don_unmatched_region) > 0){ #Only rbinds if there are any entries
  df_don_region <- rbind(
    df_don_region,
    df_don_unmatched_region)
}



```


## **WARNING** Countries and regions in non-standard format - Please edit the DON tracker or the Product Tracker to correct these

:::: {.columns}
::: {.column}

The following entries in the DON Tracker do not have a region:

```{r, results='asis', ft.align='left', ft.top=2.8}
# Rendering Flextable
df_don_unmatched %>% 
  filter(is.na(region)) %>% 
  select(ID, disease, country, region) %>% 
  flextable() %>% 
  width(j=1:4, width=1)

```

:::
::: {.column}
The following countries have non-standard names that are not recognized, please check the product tracker:

* `r paste(paste0('(', 1:length(unmatched_countries),') ', unmatched_countries), collapse = '; ')`
:::
::::



```{r include=FALSE}
# Merge dataframe of information products
# Create data.frame with NAs if nrow of df_XXX_count_region is 0. Then remove after full_join
df_rra_count_region <- df_pt_region %>% 
  filter(RRA=='Yes') %>% 
  filter(RRA_pub_year_month >= 
           as.Date(as.yearmon(report.month)) %m-% months(4) &
           RRA_pub_year_month < 
           as.Date(as.yearmon(report.month)) %m+% months(2)) %>% 
  group_by (RRA_pub_year_month) %>% 
  summarise(sum.rra.region=n())

if(nrow(df_rra_count_region)==0){
  df_rra_count_region <- data.frame(
    RRA_pub_year_month = df_prod_count$pub_year_month,
    sum.rra.region = rep(0, times=length(df_prod_count$pub_year_month))
  )
}

df_eis_count_region <- df_pt_region %>% 
  filter(EIS=='Yes') %>%
  filter(EIS_pub_year_month >= 
           as.Date(as.yearmon(report.month)) %m-% months(4) &
           EIS_pub_year_month < 
           as.Date(as.yearmon(report.month)) %m+% months(2)) %>% 
  group_by(EIS_pub_year_month) %>% 
  summarise(sum.eis.region=n())

if(nrow(df_eis_count_region)==0){
  df_eis_count_region <- data.frame(
    EIS_pub_year_month = df_prod_count$pub_year_month,
    sum.eis.region = rep(0, times=length(df_prod_count$pub_year_month))
  )
}

df_don_count_region <- df_don_region %>% 
  filter(status=='Published') %>% 
  filter(DON_pub_year_month >= 
           as.Date(as.yearmon(report.month)) %m-% months(4) &
           DON_pub_year_month < 
           as.Date(as.yearmon(report.month)) %m+% months(2)) %>% 
  filter(!is.na(DON_pub_year_month)) %>% 
  group_by (DON_pub_year_month) %>% 
  summarise(sum.don.region=n())

if(nrow(df_don_count_region)==0){
  df_don_count_region <- data.frame(
    DON_pub_year_month = df_prod_count$pub_year_month,
    sum.don.region = rep(0, times=length(df_prod_count$pub_year_month))
  )
}

#rename colnames
colnames(df_rra_count_region)[1] <- 'pub_year_month'
colnames(df_eis_count_region)[1] <- 'pub_year_month'
colnames(df_don_count_region)[1] <- 'pub_year_month'

# create new dataframe
df_prod_count_region <- df_eis_count_region %>% 
  full_join(df_rra_count_region, 
            by='pub_year_month') %>% 
  full_join(df_don_count_region, 
            by='pub_year_month') 


# Overall
df_prod_count_region <- right_join(df_prod_count_region, df_prod_count, by='pub_year_month') %>%
  filter(pub_year_month < as.Date(as.yearmon(report.month)) %m+% months(2))
df_prod_count_region[is.na(df_prod_count_region)] <- 0
df_prod_count_region <- df_prod_count_region %>%
  mutate(current.region = sum.eis.region + sum.rra.region + sum.don.region)
df_prod_count_region <- df_prod_count_region %>% 
  mutate(percentage=round(current.region/total*100,0), 
         eis.percentage=round(sum.eis.region/sum.eis*100,0),
         rra.percentage=round(sum.rra.region/sum.rra*100,0),
         don.percentage=round(sum.don.region/sum.don*100,0))

```


## WHO `r selected.region`: Bar chart of products over time - by product

::: columns
::: column
```{r fig.width=3.75, fig.height=4}
# Create dataframe
df_fig_count_region <- df_prod_count_region %>% 
  select(pub_year_month, sum.eis.region ,sum.rra.region, sum.don.region, current.region) %>%  
  filter(pub_year_month >= 
           as.Date(as.yearmon(report.month)) %m-% months(4) &
           pub_year_month < 
           as.Date(as.yearmon(report.month)) %m+% months(2)) %>% 
  gather(key='product', value='number', 2:5) %>% 
  mutate(product = case_when(
    product == 'sum.eis.region' ~ 'EIS published',
    product == 'sum.rra.region' ~ 'RRA published',
    product == 'sum.don.region' ~ 'DON published',
    product == 'current.region' ~ 'All information products published'
  ),
  product = factor(product, levels = c("All information products published", 
                                       "RRA published", 
                                       "EIS published", 
                                       "DON published")))

df_fig_count_region_per <- df_prod_count_region %>% select(pub_year_month,eis.percentage,rra.percentage,don.percentage, percentage) %>%  
  filter(pub_year_month < as.Date(as.yearmon(report.month)) %m+% months(2)) %>% 
  gather( key='product', value='number', 2:5) %>% 
  mutate(product = case_when(
    product == 'eis.percentage' ~ 'EIS published (% of all globally)',
    product == 'rra.percentage' ~ 'RRA published (% of all globally)',
    product == 'don.percentage' ~ 'DON published (% of all globally)',
    product == 'percentage' ~ 'All information products published (% of all globally)'
  ),
  product = factor(product, levels = c(
    "All information products published (% of all globally)", 
    "RRA published (% of all globally)", 
    "EIS published (% of all globally)", 
    "DON published (% of all globally)")))


# Create figures information products published over time
fig_infoprod_region <- df_fig_count_region  %>% 
  ggplot(aes(x = pub_year_month, y = number)) +
  geom_bar(stat='identity', colour='black', fill='#0072B2') +
  geom_text(aes(label = number, vjust=-0.4) ) +
  scale_x_date(date_breaks = '1 month', date_labels = '%b %y') +
  expand_limits(y=c(0, max(df_fig_count_region$number) + 5)) +
  labs(x='', y='Number') +
  facet_wrap(.~product, nrow = 4) +
  theme_bw() +
  theme(legend.position='none',
        axis.ticks=element_blank())

fig_infoprod_region

```
:::
::: column
```{r, results='asis', fig.width=3.75, fig.height=4}
# create figures information products published over time
fig_infoprod_region_per <- df_fig_count_region_per %>% 
  ggplot(aes(x = pub_year_month, y = number)) +
  geom_bar(stat='identity', colour='black', fill='#0072B2') +
  geom_text(aes(label = number, vjust=-0.4) ) +
  scale_x_date(date_breaks = '1 month', date_labels = '%b %y') +
  expand_limits(y=c(0,100)) +
  labs(x='', y='Percentage') +
  facet_wrap(.~product, nrow = 4) +
  theme_bw() +
  theme(legend.position='none',
        axis.ticks=element_blank())

fig_infoprod_region_per

```

:::
:::



## WHO `r selected.region`: Data by disease and month-year
```{r include=FALSE}
months <- unique(df_eis_time %>% 
                   filter(EIS_pub_year_month > 
                            as.Date(as.yearmon(report.month)) %m-% months(4) & 
                            EIS_pub_year_month < 
                            as.Date(as.yearmon(report.month)) %m+% months(2)) %>%
                   rename(pub_year_month = EIS_pub_year_month)) %>% 
  select(pub_year_month) %>% 
  arrange(pub_year_month) %>% 
  distinct_all()



df_rra_dy_count_region <- df_pt_region %>% 
  filter(RRA=='Yes') %>% 
  filter(RRA_pub_year_month >= 
           as.Date(as.yearmon(report.month)) %m-% months(4) &
           RRA_pub_year_month < 
           as.Date(as.yearmon(report.month)) %m+% months(2)) %>% 
  group_by (RRA_pub_year_month, disease) %>% 
  summarise(sum.rra=n()) %>% 
  rename(pub_year_month = RRA_pub_year_month) %>% 
  right_join(months, by='pub_year_month') %>% 
  arrange(pub_year_month) %>% 
  mutate(sum.rra = ifelse(is.na(sum.rra), 0, sum.rra)) %>% 
  filter(!(is.na(disease) & sum.rra==0))


df_eis_dy_count_region <- df_pt_region %>% 
  filter(EIS=='Yes') %>%
  filter(EIS_pub_year_month >= 
           as.Date(as.yearmon(report.month)) %m-% months(4) &
           EIS_pub_year_month < 
           as.Date(as.yearmon(report.month)) %m+% months(2)) %>% 
  group_by (EIS_pub_year_month, disease) %>% 
  summarise(sum.eis=n()) %>% 
  rename(pub_year_month = EIS_pub_year_month) %>% 
  right_join(months, by='pub_year_month') %>% 
  arrange(pub_year_month) %>% 
  mutate(sum.eis = ifelse(is.na(sum.eis), 0, sum.eis)) %>% 
  filter(!(is.na(disease) & sum.eis==0))


df_don_dy_count_region <- df_don_region %>% 
  filter(status=='Published') %>% 
  filter(DON_pub_year_month >= 
           as.Date(as.yearmon(report.month)) %m-% months(4) &
           DON_pub_year_month < 
           as.Date(as.yearmon(report.month)) %m+% months(2)) %>% 
  filter(!is.na(DON_pub_year_month)) %>% 
  group_by (DON_pub_year_month, disease) %>% 
  summarise(sum.don=n()) %>% 
  rename(pub_year_month = DON_pub_year_month) %>% 
  right_join(months, by='pub_year_month') %>% 
  arrange(pub_year_month) %>% 
  mutate(sum.don = ifelse(is.na(sum.don), 0, sum.don)) %>% 
  filter(!(is.na(disease) & sum.don==0))


# Rename values in disease column
df_rra_dy_count_region$disease[str_sub(df_rra_dy_count_region$disease, 1,5)=="Avian"] <- "Avian influenza"
df_rra_dy_count_region$disease[str_sub(df_rra_dy_count_region$disease, 1,5)=="Shige"] <- "Shigellosis"
df_rra_dy_count_region$disease[str_sub(df_rra_dy_count_region$disease, 1,5)=="Crime"] <- "Crimean-Congo hemorrhagic fever"
df_rra_dy_count_region$disease[str_sub(df_rra_dy_count_region$disease, 1,5)=="Monke"] <- "mpox"
df_rra_dy_count_region$disease[str_sub(df_rra_dy_count_region$disease, 1,5)=="Lassa"] <- "Lassa fever"
df_rra_dy_count_region$disease[str_sub(df_rra_dy_count_region$disease, 1,5)=="Yello"] <- "Yellow fever"
df_rra_dy_count_region$disease[str_sub(df_rra_dy_count_region$disease, 1,5)=="Polio"] <- "Polio"
df_rra_dy_count_region$disease[str_sub(df_rra_dy_count_region$disease, 1,4)=="Wild"] <- "Polio"
df_rra_dy_count_region$disease[df_rra_dy_count_region$disease=="Hepatitis (unspecified)"] <- "Acute hepatitis of unknown aetiology"
df_rra_dy_count_region$disease[df_rra_dy_count_region$disease=="Nipah virus disease"] <- "Nipah" 
df_rra_dy_count_region$disease[df_rra_dy_count_region$disease=="Enterovirus Infection (E-11)"] <- "Enterovirus" 
df_rra_dy_count_region$disease[df_rra_dy_count_region$disease=="Myocarditis"] <- "Neonatal myocarditis"

df_eis_dy_count_region$disease[str_sub(df_eis_dy_count_region$disease, 1,5)=="Avian"] <- "Avian influenza"
df_eis_dy_count_region$disease[str_sub(df_eis_dy_count_region$disease, 1,5)=="Swine"] <- "Swine influenza"
df_eis_dy_count_region$disease[str_sub(df_eis_dy_count_region$disease, 1,5)=="Influ"] <- "Avian influenza"
df_eis_dy_count_region$disease[str_sub(df_eis_dy_count_region$disease, 1,5)=="Shige"] <- "Shigellosis"
df_eis_dy_count_region$disease[str_sub(df_eis_dy_count_region$disease, 1,5)=="Crime"] <- "Crimean-Congo hemorrhagic fever"
df_eis_dy_count_region$disease[str_sub(df_eis_dy_count_region$disease, 1,5)=="Polio"] <- "Polio"
df_eis_dy_count_region$disease[str_sub(df_eis_dy_count_region$disease, 1,4)=="Wild"] <- "Polio"
df_eis_dy_count_region$disease[str_sub(df_eis_dy_count_region$disease, 1,5)=="Monke"] <- "mpox"
df_eis_dy_count_region$disease[str_sub(df_eis_dy_count_region$disease, 1,5)=="Yello"] <- "Yellow fever"
df_eis_dy_count_region$disease[df_eis_dy_count_region$disease=="Acute febrile jaundice syndrome"] <- "Acute hepatitis of unknown aetiology"
df_eis_dy_count_region$disease[df_eis_dy_count_region$disease=="Hepatitis (unspecified)"] <- "Acute hepatitis of unknown aetiology"
df_eis_dy_count_region$disease[df_eis_dy_count_region$disease=="Nipah virus disease"] <- "Nipah" 
df_eis_dy_count_region$disease[df_eis_dy_count_region$disease=="Enterovirus Infection (E-11)"] <- "Enterovirus" 
df_eis_dy_count_region$disease[df_eis_dy_count_region$disease=="Myocarditis"] <- "Neonatal myocarditis"

df_don_dy_count_region$disease[str_sub(df_don_dy_count_region$disease, 1,5)=="Dengu"] <- "Dengue"
df_don_dy_count_region$disease[str_sub(df_don_dy_count_region$disease, 1,5)=="Influ"] <- "Avian influenza"
df_don_dy_count_region$disease[str_sub(df_don_dy_count_region$disease, 1,5)=="Infue"] <- "Avian influenza"
df_don_dy_count_region$disease[str_sub(df_don_dy_count_region$disease, 1,5)=="Avian"] <- "Avian influenza"
df_don_dy_count_region$disease[str_sub(df_don_dy_count_region$disease, 1,5)=="Monke"] <- "mpox"
df_don_dy_count_region$disease[str_sub(df_don_dy_count_region$disease, 1,5)=="Lassa"] <- "Lassa fever"
df_don_dy_count_region$disease[str_sub(df_don_dy_count_region$disease, 1,5)=="Circu"] <- "Polio"
df_don_dy_count_region$disease[str_sub(df_don_dy_count_region$disease, 1,4)=="Wild"] <- "Polio"
df_don_dy_count_region$disease[str_sub(df_don_dy_count_region$disease, 1,5)=="Wild "] <- "Polio"
df_don_dy_count_region$disease[str_sub(df_don_dy_count_region$disease, 1,5)=="cVDPV"] <- "Polio"
df_don_dy_count_region$disease[str_sub(df_don_dy_count_region$disease, 1,5)=="WPV1"] <- "Polio"
df_don_dy_count_region$disease[str_sub(df_don_dy_count_region$disease, 1,5)=="Marbu"] <- "Marburg"
df_don_dy_count_region$disease[str_sub(df_don_dy_count_region$disease, 1,3)=="XDR"] <- "Shigellosis"
df_don_dy_count_region$disease[str_sub(df_don_dy_count_region$disease, 1,5)=="Yello"] <- "Yellow fever"
df_don_dy_count_region$disease[df_don_dy_count_region$disease=="Acute hepatitis of unknown aetiology in children - Multi-country"] <- "Acute hepatitis of unknown aetiology"
df_don_dy_count_region$disease[df_don_dy_count_region$disease=="Sudan Virus disease"] <- "Sudan virus disease"
df_don_dy_count_region$disease[df_don_dy_count_region$disease=="Invasive Group A Streptococcus infection"] <- "Scarlet fever and invasive Group A Streptococcus infection"
df_don_dy_count_region$disease[df_don_dy_count_region$disease=="Nipah virus disease"] <- "Nipah" 
df_don_dy_count_region$disease[df_don_dy_count_region$disease=="Enterovirus Infection (E-11)"] <- "Enterovirus" 
df_don_dy_count_region$disease[df_don_dy_count_region$disease=="Myocarditis"] <- "Neonatal myocarditis"

# create new dataframe
df_prod_dy_count_region <- df_eis_dy_count_region %>% 
  full_join(df_rra_dy_count_region, by=c('pub_year_month', 'disease')) %>%
  full_join(df_don_dy_count_region, by=c('pub_year_month', 'disease')) %>% 
  mutate(sum.rra = ifelse(is.na(sum.rra), 0, sum.rra),
         sum.eis = ifelse(is.na(sum.eis), 0, sum.eis),
         sum.don = ifelse(is.na(sum.don), 0, sum.don))

# df_prod_dy_count_region[is.na(df_prod_dy_count_region)] <- 0

df_prod_dy_count_region <- df_prod_dy_count_region %>%
  mutate(total=sum.eis+sum.rra+sum.don)

```

```{r fig.width=35, fig.height=20}

date.levels <- as.Date(seq.Date(from = as.Date(as.yearmon(report.month)) %m-% months(4), 
                                to = as.Date(as.yearmon(report.month)) %m+% months(1), 
                                by = "month"), format = '%d/%m/%Y')


# Create dataframe
df_fig_dy_count_region <- df_prod_dy_count_region %>% 
  filter(pub_year_month < as.Date(as.yearmon(report.month)) %m+% months(2)) %>% 
  gather(key='product', value='Number', 3:6) %>% 
  right_join(., data.frame(pub_year_month=date.levels), by='pub_year_month') %>% 
  mutate(disease = ifelse(is.na(disease), '', disease),
         product = case_when(
           product == 'sum.eis' ~ 'EIS',
           product == 'sum.rra' ~ 'RRA',
           product == 'sum.don' ~ 'DON',
           product == 'total' ~ 'All info products'
         ),
         product = ifelse(is.na(product), 'All info products', product),
         product = factor(product, levels = c("All info products", 
                                              "RRA", 
                                              "EIS", 
                                              "DON")),
         Number = ifelse(is.na(Number), 0, Number))


df_fig_dy_count_region$disease <- factor(df_fig_dy_count_region$disease,
                                         levels = rev(sort(unique(df_fig_dy_count_region$disease))))


# Heatmap
Fig_heatmap_prod_region <- df_fig_dy_count_region %>% 
  ggplot(aes(pub_year_month, disease, fill=Number)) +
  geom_tile(color='white', 
            size=0.1, 
            height=ifelse(length(unique(df_fig_dy_count_region$disease)) <= 5, 0.5, 0.2)) + 
  scale_x_date(date_breaks = '1 month', date_labels = '%b %y') +
  labs(x='', y='') +
  facet_wrap(.~product, nrow = 1) +
  scale_fill_gradient(low = 'white', high = '#0072B2') +
  theme_bw() +
  theme(axis.ticks=element_blank(),
        axis.text.x=element_text(angle=45, hjust=1.1, size=35),
        axis.text.y=element_text(size=40),
        panel.grid.major = element_blank(),
        strip.text = element_text(size=40),
        legend.key.size = unit(1.25, 'in'),
        legend.title = element_text(size=35),
        legend.text = element_text(size=35))

Fig_heatmap_prod_region

```



```{r}
# Get months to assess
months <- unique(df_eis_time %>% 
                   filter(EIS_pub_year_month >= 
                            as.Date(as.yearmon(report.month)) %m-% months(4) &
                            EIS_pub_year_month < 
                            as.Date(as.yearmon(report.month)) %m+% months(2)) %>% 
                   pull(EIS_pub_year_month))

```




## WHO `r selected.region`: Key trends info products – `r paste0(format(as.Date(as.yearmon(report.month)) %m-% months(4), '%b %Y'), '-', format(as.Date(as.yearmon(report.month)) %m+% months(1), '%b %Y'))`

* **Information products** (RRA, EIS, DON) from **`r selected.region`** make up **XX-XX**% of **all information products globally** per month between `r paste0(format(as.Date(as.yearmon(report.month)) %m-% months(4), '%b %Y'), '-', format(as.Date(as.yearmon(report.month)) %m+% months(1), '%b %Y'))`.

\ 

* The **events** in **`r selected.region`** which **required** an **EIS, RRA or DON** were **related** to **[INSERT DISEASES HERE]** in the period `r paste0(format(as.Date(as.yearmon(report.month)) %m-% months(4), '%b %Y'), '-', format(as.Date(as.yearmon(report.month)) %m+% months(1), '%b %Y'))`.

\ 

* In addition, **`r selected.region`** colleagues were involved in **regional or global information products** on **[INSERT DISEASES HERE]** as well as contributing to **global RRAs** for **[INSERT DISEASES HERE]** in the period `r paste0(format(as.Date(as.yearmon(report.month)) %m-% months(4), '%b %Y'), '-', format(as.Date(as.yearmon(report.month)) %m+% months(1), '%b %Y'))`.

\ 

* Moreover, **`r selected.region`** is involved in several other information products. **Information products**, such as **PHSA**, are **not shown in previous slides**.



## WHO `r selected.region`: Timeliness RRA, EIS, DON – `r paste0(format(as.Date(as.yearmon(report.month)) %m-% months(4), '%b %y'), '-', format(as.Date(as.yearmon(report.month)) %m+% months(1), '%b %y'))`

```{r}
# RRA
# Create dataframe and create variable time between decision and publication
df_rra_time_region <- df_pt_region %>% 
  filter(RRA=='Yes') %>%
  mutate(time_rra=as.numeric(RRA_date_publication-RRA_date_decision)) %>% 
  data.frame() %>%
  filter(RRA_pub_year_month!='1990-01-01') %>% 
  filter(RRA_pub_year_month > as.Date(as.yearmon(report.month)) %m-% months(4) & 
           RRA_pub_year_month < as.Date(as.yearmon(report.month)) %m+% months(2)) 


# Detect if all months are present
rra.missing.months <- as.Date(
  setdiff(months, 
          unique(df_rra_time_region$RRA_pub_year_month)))

# Add row with 0 value for missing month
if(length(rra.missing.months) > 0){
  df_rra_time_region <- df_rra_time_region %>%
    add_row(RRA_pub_year_month = rra.missing.months, 
            time_rra=rep(NA, times=length(rra.missing.months)))
}

```

```{r}
# EIS
#create dataframe and create variable time between decision and publication
df_eis_time_region <- df_pt_region %>% 
  filter(EIS=='Yes',
         EIS_date_publication != '1990-01-01') %>%
  mutate(time_eis=as.numeric(EIS_date_publication-EIS_date_decision)) %>%
  data.frame()  %>% 
  filter(EIS_pub_year_month > as.Date(as.yearmon(report.month)) %m-% months(4) & 
           EIS_pub_year_month < as.Date(as.yearmon(report.month)) %m+% months(2))


# Detect if all months are present
eis.missing.months <- as.Date(
  setdiff(months, 
          unique(df_eis_time_region$EIS_pub_year_month)))

# Add row with 0 value for missing month
if(length(eis.missing.months) > 0){
  df_eis_time_region <- df_eis_time_region %>%
    add_row(EIS_pub_year_month = eis.missing.months, 
            time_eis=rep(NA, times=length(eis.missing.months)))
}

```

```{r}
# DON
#create time variable
df_don_time_region <- df_don_region %>% 
  filter(status=='Published') %>% 
  filter(DON_pub_year_month > as.Date(as.yearmon(report.month)) %m-% months(4) & 
           DON_pub_year_month < as.Date(as.yearmon(report.month)) %m+% months(2)) %>% 
  mutate(time_don=as.numeric(DON_date_publication-EIS_date_publication))

# Detect if all months are present
don.missing.months <- as.Date(
  setdiff(months, 
          unique(df_don_time_region$DON_pub_year_month)))

# Add row with 0 value for missing month
if(length(don.missing.months) > 0){
  df_don_time_region <- df_don_time_region %>%
    add_row(DON_pub_year_month = don.missing.months, 
            time_don=rep(NA, times=length(don.missing.months)))
}
```


```{r}
# RRA timeliness
rra.timeliness <- merge(
  data.frame(Month = months),
  df_rra_time_region %>% 
    select(RRA_pub_year_month, time_rra),
  by.x='Month', 
  by.y='RRA_pub_year_month'
) %>%
  data.frame(.) %>%
  group_by(Month) %>%
  summarize(
    rra.n = n(),
    rra.median = median(time_rra, na.rm = TRUE),
    rra.iqr = paste0(round(as.numeric(quantile(time_rra, probs=c(0.25), 
                                               na.rm=TRUE)), 0),
                     '-',
                     round(as.numeric(quantile(time_rra, probs=c(0.75), 
                                               na.rm=TRUE)), 0)),
    rra.min.max = paste0(min(time_rra),'-',max(time_rra))
  ) %>%
  mutate(Month = format(as.Date(Month), '%b %Y'),
         rra.n = ifelse(is.na(rra.median), 0, rra.n),
         rra.median = ifelse(is.na(rra.median), '-', rra.median),
         rra.iqr = str_replace_all(rra.iqr, 'NA', ''),
         rra.iqr = ifelse(rra.n==1, '-', rra.iqr),
         rra.min.max = str_replace_all(rra.min.max, 'NA', ''),
         rra.min.max = ifelse(rra.n==1, '-', rra.min.max))


# EIS timeliness
eis.timeliness <- merge(
  data.frame(Month = months),
  df_eis_time_region %>% 
    select(EIS_pub_year_month, time_eis),
  by.x='Month', 
  by.y='EIS_pub_year_month'
) %>%
  data.frame(.) %>%
  group_by(Month) %>%
  summarize(
    eis.n = n(),
    eis.median = median(time_eis, na.rm = TRUE),
    eis.iqr = paste0(round(as.numeric(quantile(time_eis, probs=c(0.25), 
                                               na.rm=TRUE)), 0),
                     '-',
                     round(as.numeric(quantile(time_eis, probs=c(0.75), 
                                               na.rm=TRUE)), 0)),
    eis.min.max = paste0(min(time_eis),'-',max(time_eis))
  ) %>%
  mutate(Month = format(as.Date(Month), '%b %Y'),
         eis.n = ifelse(is.na(eis.median), 0, eis.n),
         eis.median = ifelse(is.na(eis.median), '-', eis.median),
         eis.iqr = str_replace_all(eis.iqr, 'NA', ''),
         eis.iqr = ifelse(eis.n==1, '-', eis.iqr),
         eis.min.max = str_replace_all(eis.min.max, 'NA', ''),
         eis.min.max = ifelse(eis.n==1, '-', eis.min.max))


# DON timeliness
don.timeliness <- merge(
  data.frame(Month = months),
  df_don_time_region %>% 
    select(DON_pub_year_month, time_don),
  by.x='Month', 
  by.y='DON_pub_year_month'
) %>%
  data.frame(.) %>%
  group_by(Month) %>%
  summarize(
    don.n = n(),
    don.median = median(time_don, na.rm = TRUE),
    don.iqr = paste0(round(as.numeric(quantile(time_don, probs=c(0.25), 
                                               na.rm=TRUE)), 0),
                     '-',
                     round(as.numeric(quantile(time_don, probs=c(0.75), 
                                               na.rm=TRUE)), 0)),
    don.min.max = paste0(min(time_don),'-',max(time_don))
  ) %>%
  mutate(Month = format(as.Date(Month), '%b %Y'),
         don.n = ifelse(is.na(don.median), 0, don.n),
         don.median = ifelse(is.na(don.median), '-', don.median),
         don.iqr = str_replace_all(don.iqr, 'NA', ''),
         don.iqr = ifelse(don.n==1, '-', don.iqr),
         don.min.max = str_replace_all(don.min.max, 'NA', ''),
         don.min.max = ifelse(don.n==1, '-', don.min.max))


# Timeliness all
timeliness.all <- cbind(rra.timeliness,
                        eis.timeliness %>% select(-Month),
                        don.timeliness %>% select(-Month))

```

* **Timeliness** for **all information products** related to **`r selected.region` were generally in excess of X days**.
- **RRA timeliness* ** (`r sum(timeliness.all$rra.n)` RRA reports) - **median** timeliness ranged from `r min(as.numeric(timeliness.all$rra.median), na.rm = T)`-`r max(as.numeric(timeliness.all$rra.median), na.rm = T)` days 
- **EIS timeliness* ** (`r sum(timeliness.all$eis.n)` EIS postings) - **median** timeliness ranged from `r min(as.numeric(timeliness.all$eis.median), na.rm = T)`-`r max(as.numeric(timeliness.all$eis.median), na.rm = T)` days 
- **DON timeliness* ** (`r sum(timeliness.all$don.n)` DON reports)  - **median** timeliness ranged from `r min(as.numeric(timeliness.all$don.median), na.rm = T)`-`r max(as.numeric(timeliness.all$don.median), na.rm = T)` days 

\ 
\ 
\ 
\ 

*Timeliness was measured as time between decision to do an RRA or EIS and date of publication or time between EIS publication and DON publication. 



## WHO `r selected.region`: Timeliness Summary Metrics

```{r}
# Flextable for plot
timeliness.all %>%
  flextable() %>%
  set_header_labels(values = list(
    rra.n = 'N',
    rra.median = 'Median',
    rra.iqr = 'IQR',
    rra.min.max = 'Min-Max',
    eis.n = 'N',
    eis.median = 'Median',
    eis.iqr = 'IQR',
    eis.min.max = 'Min-Max',
    don.n = 'N',
    don.median = 'Median',
    don.iqr = 'IQR',
    don.min.max = 'Min-Max'
  )) %>%
  flextable::align(j=2:10, align='center', part='all') %>%
  add_header_row(values = c('', 'RRA','RRA','RRA','RRA',
                            'EIS','EIS','EIS','EIS',
                            'DON','DON','DON','DON'), top = TRUE) %>%
  merge_h(part = 'header') %>%
  width(j=1, width=2)

```




```{r, eval=FALSE}
knitr::asis_output('## RRA timeliness')

```

```{r, eval=FALSE}
# RRA
# Create Figure over time in the last 6 months
Fig_RRA_time_region_box <- df_rra_time_region  %>% 
  arrange(RRA_pub_year_month) %>%
  mutate(RRA_pub_year_month = format(RRA_pub_year_month, '%b %y')) %>% 
  ggplot(aes(x=forcats::fct_inorder(RRA_pub_year_month), y=as.numeric(time_rra))) +
  geom_boxplot(fill='#0072B2') +
  labs(x='Date', y='Time (days)') +
  scale_x_discrete(drop=FALSE)+
  scale_fill_discrete(drop=FALSE) +
  scale_y_continuous(breaks=seq(0, 110, 20)) +  # Ticks from 0-60, every 5
  theme_bw() +
  theme(axis.text.x=element_text(angle=45, hjust=1)) +
  geom_hline(yintercept = 7, linetype='dashed', color='red')

knitr::knit_print(Fig_RRA_time_region_box)

```



```{r, eval=FALSE}
knitr::asis_output('## EIS timeliness')

```

```{r, eval=FALSE}
# Create Figure over time in the last 6 months
Fig_EIS_time_region_box <- df_eis_time_region %>% 
  arrange(EIS_pub_year_month) %>% 
  mutate(EIS_pub_year_month = format(EIS_pub_year_month, '%b %y')) %>% 
  # mutate(time_eis = ifelse(is.na(time_eis), 0, as.numeric(time_eis))) %>%
  ggplot(aes(x=forcats::fct_inorder(EIS_pub_year_month), y=as.numeric(time_eis))) +
  geom_boxplot(fill='#0072B2', position=position_dodge(preserve = "single")) +
  labs(x='Date', y='Time (days)') +
  # scale_x_date(date_breaks = '1 month', date_labels = '%b %y') +
  scale_x_discrete(drop=FALSE)+
  scale_fill_discrete(drop=FALSE) +
  # scale_y_continuous(breaks=seq(0, 80, 5)) +  # Ticks from 0-60, every 5
  theme_bw() +
  theme(axis.text.x=element_text(angle=45, hjust=1)) +
  geom_hline(yintercept = 4, linetype='dashed', color='red')

Fig_EIS_time_region_box

```


```{r, eval=FALSE}
knitr::asis_output('## DON timeliness')

```

```{r, eval=FALSE}
# Create Figure over time in the last 6 months
Fig_DON_time_box_region <-  df_don_time_region %>% 
  arrange(DON_pub_year_month) %>% 
  mutate(DON_pub_year_month = format(DON_pub_year_month, '%b %y')) %>% 
  ggplot(aes(x=forcats::fct_inorder(DON_pub_year_month), y=as.numeric(time_don))) +
  geom_boxplot(fill='#0072B2') +
  labs(x='Date', y='Time (days)') +
  scale_x_discrete(drop=FALSE)+
  scale_fill_discrete(drop=FALSE) +
  scale_y_continuous(breaks=seq(0, 45, 5)) +  # Ticks from 0-60, every 5
  theme_bw() +
  theme(axis.text.x=element_text(angle=45, hjust=1)) +
  geom_hline(yintercept = 5, linetype='dashed', color='red')

Fig_DON_time_box_region

```

